\chapter{\label{ch:1-intro}Introduction} 

% \minitoc

Since the discovery of neutrino flavour oscillations, which implies that
neutrinos have mass, neutrino physics has enjoyed a period of rapid development.
The field has begun to transition into an era of precision, with many of the
parameters governing these oscillations having been well constrained. The fact
that neutrinos have mass, and the success of the PMNS theory in describing
neutrino oscillations, leads to a number of fundamental questions which have
important implications in both particle physics and cosmology: 

\begin{itemize}
	\item What is the mechanism giving rise to neutrino mass? 
	\item Are neutrinos Dirac or Majorana particles?
	\item What is the absolute scale and ordering of the neutrino masses?
	\item Do neutrinos and anti--neutrinos oscillate differently, and would this 
	      help to explain the matter anti--matter asymmetry in the universe?
\end{itemize}

In addition to these questions from the neutrino physics community, the high
resolution and large masses of modern neutrino detectors make them useful tools
for both astronomy and astrophysics. 2017 has widely been considered as the dawn
of multi--messenger astronomy, with a measurement of gravitational waves at LIGO
being correlated with measurements of a neutron star merger from electromagnetic
telescopes \cite{Abbott2017}. This measurement was shortly followed by a similar
correlation but in the neutrino sector between a high energy neutrino event in
ICECUBE and a number of traditional telescopes \cite{Aartsen2018}. Within our
galaxy, neutrino detectors provide a unique opportunity to understand the
underlying mechanisms in supernovae; in the case of such a supernova, the
structure of the neutrino flux at earth provides a mechanism to measure effects
in the early stages of the supernova burst which are inaccessible with
electromagnetic measurements \cite{Scholberg:2012id}.

Each of these questions places unique constraints on the design of an
appropriate neutrino detector. The discovery of a matter anti--matter asymmetry
in neutrino oscillations can be answered by making precise measurements of
neutrino oscillations. This requires reliably identifying the flavour and energy
of neutrinos in order to measure the appearance and disappearance spectra
associated with neutrinos produced in long baseline neutrino experiments. To
identify the low energy electrons produced in supernova neutrino interactions, a
detector with low thresholds and low backgrounds is required. The Deep
Underground Neutrino Experiment (DUNE) aims to tackle these challenges by
utilising the Liquid Argon Time Projection Chamber (LArTPC) technology, whose
high spatial and calorimetric resolution allows for more accurate topological
classification of neutrino interactions \cite{Acciarri:2016crz}. To achieve
these goals, a significant programme of LArTPC research is ongoing with
construction, reconstruction, and analysis methods all under development in a
number of LArTPC based experiments \cite{Acciarri:2016smi, Cavanna:2014iqa,
Antonello:2015lea, Abi:2017aow}. 

This thesis presents an analysis of charged particle interactions in the
ProtoDUNE--SP LArTPC detector. A hit classification algorithm is developed and a
sample of Michel electrons is used to provide a measurement of electron energy
bias for low energy electrons. The analysis described in this thesis uses data
collected with the ProtoDUNE--SP detector between August and November 2018.

Michel electrons have an energy spectrum spanning 0--60 MeV; understanding
electrons in this energy range is important as they are the same energy as those
produced when neutrinos from supernova bursts interact. In a LArTPC at these
energies, the energy deposition of electrons transitions between ionisation
dominated and radiation dominated regimes making for a particularly complicated
combined event topology \cite{Acciarri:2017sjy}. The work presented here details
a reconstruction strategy based on augmenting hit identification from a
convolution neural network with simple clustering to identify and reconstruct
Michel electron events. Analysis of these Michel electron events in
ProtoDUNE--SP data and simulation quantifies the energy scale and energy scale
bias for low energy electrons in a surface level LArTPC detector; this
measurement can provide valuable input to studies of supernova burst neutrinos
in LArTPC detectors.

Chapter \ref{ch:2-neutrinophysics} provides a theoretical overview of neutrinos
within the standard model. Interactions, oscillations, and production will be
discussed summarising the current knowledge in the field, as well as open
questions which will be studied in ongoing and upcoming experiments. The role of
neutrinos in supernova bursts and the detection of such neutrinos in a LArTPC
detector will be discussed in more detail.

The ProtoDUNE--SP experiment is described in chapter \ref{ch:3-protodune},
including details of the beam line, detector, cosmic ray flux, and simulations.
An overview of the LArTPC detection principle will be given with specific
details of the ProtoDUNE--SP design. Some details of detector operations will be
discussed, paying particular attention to the monitoring of the detector via the
online data quality monitoring system.

Chapter \ref{ch:4-energyloss} will cover details of electromagnetic energy loss
in liquid argon. Electron and photon energy loss will be discussed as well as
processes leading to electron-ion recombination. The impacts of these effects on
electron reconstruction in liquid argon will be highlighted.

The main analysis of this thesis will be described in chapters
\ref{ch:5-chargeid} and \ref{ch:6-michel}. Details of a hit classification
algorithm based on convolutional neural networks will be given and Michel
electron reconstruction will be highlighted as an example use for the output of
this algorithm. Michel electron production and energy loss in liquid argon will
be discussed. This will be followed by details of the reconstruction strategy
used in the Michel electron analysis. The reconstructed Michel electron spectrum
will be compared between data and simulation, and the energy resolution and
energy scale bias for low energy electrons in the ProtoDUNE--SP detector will be
estimated. 

Chapter \ref{ch:7-implications} will analyse the implications of the results of
the Michel electron analysis for supernova neutrino physics in the DUNE
experiment; the impacts of energy scale bias on these analyses will be
investigated, and the possible performance of DUNE assuming the measured bias
will be discussed.

A summary of the results presented in this thesis will be given in chapter
\ref{ch:8-conclusions} along with a discussion of the implications of these
results for neutrino physics in LArTPC detectors.
