\chapter{\label{ch:2-neutrinophysics}Neutrino Physics} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% From my COS report

% This chapter will cover details of relevant neutrino physics for the thesis 
% project. The theoretical aspects of neutrino physics will be reviewed 
% including the theory of neutrino oscillations in the PMNS framework. 
% Neutrino production will also be discussed including details of neutrino 
% production in supernovae and the role neutrinos can have in understanding 
% the mechanics of a supernova burst
 
% The work for this section is ongoing as it is associated with the analysis 
% work in the other sections, it is expected to be completed by the end of 
% December 2019.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% TODO: References

% \minitoc

Despite being one of the most abundant particle in the universe, neutrinos are 
some of the most elusive; due to the fact that neutrinos can only interact via
the weak interaction. The history of neutrino physics is therefore strongly
connected to the discovery and study of weak interactions. Measurements by
Chadwick in 1914 showed that the energy spectrum of electrons released in
\(\beta\)--decays was continuous, this is in contrast to discrete spectra
observed in \(\alpha\) and \(\gamma\) decays, and seemingly violates
conservation of energy under the assumption of a two--body final state which was
expected at the time. In order to solve this problem, Pauli postulated that the
continuous energy spectrum could be explained if the energy released in a 
\(\beta\)--decay could be shared with an additional neutral weakly interacting 
fermion which Pauli named the neutron. Fermi later renamed Pauli's fermion to
the neutrino, after Chadwick discovered the neutron in 1932. Despite claims that
neutrinos might never be detected, neutrinos have now been discovered and they
have been found to have a number of interesting properties which were not
anticipated when neutrinos were first postulated. This chapter will detail some 
of the history and theory of neutrino's and their interactions.

In this chapter, Section \ref{nu_hist} will give a brief historical overview of 
neutrino physics, Section \ref{nu_osc} will introduce neutrino oscillations
and the theory used to describe them, while Section \ref{nu_prod} will discuss
neutrino interactions in matter as well as neutrino production. Finally Section
\ref{nu_sn} will discuss the production of neutrinos in supernovae, as well as
the role they could play in understanding supernovae.

% TODO: decide on historical vs theoretical overview or both
\section{A Brief History of Neutrino Physics} \label{nu_hist}

The first attempt to incorporate the neutrino into a theoretical model came in
1934 when Fermi presented his theory of \(\beta\)--decay, in this theory the 
neutrino takes part in a four--point interaction with the other components of 
the \(\beta\)--decay interaction. The incredible success of this theory in
explaining the observed properties of \(\beta\)--decays provided strong evidence 
for the neutrinos existence, however, in 1934 after using Fermi's  theory to 
predict the strength of neutrino interactions, H. Bethe and R. Peierls found 
that the interactions were so weak that they might never be observed, a 
prediction that held true for over 20 years.% TODO: refs

The first breakthrough in experimental neutrino physics would come in 1956. F.
Reines and C. Cowan were attempting to measure positrons produced in inverse 
\(\beta\)--decay interactions,
\begin{equation}
	\bar{\nu_e} + p \rightarrow n + e^+.
\end{equation}
A detector containing 1400 litres of liquid scintillator was used to measure the 
large flux of electron anti--neutrinos in the vicinity of the Savannah River 
nuclear reactor. They observed a large increase in the rate of positron events 
when the reactor was on when compared to when the reactor was switched off, the 
first experimental evidence for the existence of neutrinos. % TODO: ref

% \section{Neutrinos in the Standard Model} \label{nu_sm}


\section{Neutrino Oscillations} \label{nu_osc}


\section{Neutrino Interactions} \label{nu_prod}


\section{Supernova Neutrinos} \label{nu_sn}


