This thesis would not have been possible without the advice and support of many
people. I would like to start by thanking my supervisor, Alfons Weber. He has
been a brilliant advisor, and I would like to thank him in particular for all
the opportunities he has given me. Thanks also to the rest of the Oxford
Neutrino Physics group, particularly Justo Martin--Albo, whose support during 
my first year helped me to settle into the DPhil, and my fellow students -- 
Fabio, Alex, and Ciaran -- who have made the office, both physical and 
virtual, an enjoyable place to work.

\medskip\noindent
I have worked with many great collaborators from the DUNE experiment
as part of my DPhil. I'd particularly like to thank the members of the 
\protodune{} reconstruction and analysis group, who have always given 
excellent feedback on my work. Special thanks go to Dorota Stefan and Robert 
Sulej, who were incredibly supportive during the early years of my DPhil, and 
to Leigh Whitehead and Tingjun Yang, whose insightful conversations have been 
invaluable. 

\medskip\noindent
I am very fortunate to have had the chance to work at CERN for part of my DPhil,
and I would like to thank all of the members of the on--site \protodune{} 
team, especially Alex, Chris, Geoff, James, Milo, and Seb, who I thoroughly 
enjoyed working with during my time at CERN, and from whom I have learned so 
much. 

\medskip\noindent
My greatest thanks go to my friends and family for their continued support 
over the years. First, I'd like to thank Babs, whose proof reading has improved 
the clarity of this thesis considerably. Next to my friends in Oxford: to Amy, 
Rory, and Helena, who have always been there to help me relax at the end of the 
day, and to the members of Oxford Ultimate, who have been so welcoming over the 
past year, you have kept me going during the final stages.  Finally, to my 
family, who fostered a love of learning which will always be with me, and to 
Ellie, who could never understand how much her support has meant to me over the 
years.
