\chapter{\label{ch:intro}Introduction} 

\minitoc

Since the discovery of neutrino flavour oscillations, which implies that
neutrinos have mass, neutrino physics has enjoyed a period of rapid development.
The field has begun to transition into an era of precision, with many of the
parameters governing these oscillations having been well constrained. The fact
that neutrinos have mass, and the success of the
Pontecorvo--Maki--Nakagawa--Sakata (PMNS) theory in describing neutrino 
oscillations, leads to a number of fundamental questions which have important 
implications for both particle physics and cosmology: 
\begin{itemize}
	\item What is the mechanism giving rise to neutrino mass? 
	\item Are neutrinos Dirac or Majorana particles?
	\item What is the absolute scale and ordering of the neutrino masses?
	\item Do neutrinos and anti--neutrinos oscillate differently, and would this 
	      help to explain the matter anti--matter asymmetry in the universe?
	\item Are there any sterile neutrinos?
\end{itemize}

The high resolution and large masses of modern neutrino detectors also
make them useful tools for both astronomy and astrophysics. 2017 has widely 
been considered as the dawn of multi--messenger astronomy, with a measurement 
of gravitational waves at the Laser Interferometer Gravitational--Wave 
Observatory (LIGO) being correlated with measurements of a neutron star merger 
from electromagnetic telescopes\cite{Abbott2017}.  This measurement was 
shortly followed by a similar correlation, but in the neutrino sector, between a
high energy neutrino event in the IceCube Neutrino Observatory and a number of 
traditional telescopes\cite{Aartsen2018}.  Within our galaxy, neutrino 
detectors provide a unique opportunity to understand the underlying mechanisms 
in supernovae; in the case of such a supernova, the structure of the neutrino 
flux at earth provides a mechanism to measure effects in the early stages of 
the supernova burst, which are inaccessible with electromagnetic 
measurements\cite{Scholberg:2012id}.

Each of these questions places unique constraints on the design of an
appropriate neutrino detector. The discovery of a matter anti--matter asymmetry
in neutrino oscillations could be answered by making precise measurements of
neutrino oscillations. This requires reliably identifying the flavour and energy
of neutrinos in order to measure the appearance and disappearance spectra
associated with neutrinos produced in long baseline neutrino experiments. To
identify the low energy electrons produced in supernova neutrino interactions, a
detector with low thresholds and low backgrounds is required. The Deep
Underground Neutrino Experiment (DUNE) aims to tackle these challenges by
utilising the liquid argon time projection chamber (LArTPC) technology, whose
high spatial and calorimetric resolution allows for more accurate geometric
classification of neutrino interactions. To achieve these goals, a significant 
programme of LArTPC research is ongoing with construction, reconstruction, and 
analysis methods all under development in a number of LArTPC based 
experiments\cite{Acciarri:2016smi, Cavanna:2014iqa, Antonello:2015lea, 
Abi:2017aow}. 

This thesis presents analyses of charged particle interactions in the
\protodune{} LArTPC detector, using data collected during with a test beam 
between August and November 2018. Hit classification and Michel electron 
reconstruction are investigated, and a sample of Michel electrons is used to 
provide a measurement of the energy resolution and bias for low energy 
electrons in \protodune{}.

Particle classification plays an important role in event reconstruction in 
LArTPC detectors. In particular, the clustering of hits into tracks and 
showers is an important step in reconstructing events in a LArTPC. After tracks
and showers have been reconstructed, they can be combined to build up a picture
of the full particle interaction. This thesis presents the results of the 
development of a hit classification algorithm based on convolutional neural
networks. The primary goal of this algorithm is to classify hits as 
track--like or shower--like on a hit--by--hit basis. The output from the hit 
classification has been applied to analyses of beam particle interactions, 
such as pion cross--section analyses, and cosmic--ray interactions, which 
are used to calibrate the \protodune{} detector. These outputs are also used 
to select a sample of Michel electron candidates, which are also analysed in 
this thesis.

Michel electrons have an energy spectrum spanning 0--60 MeV. Understanding
electrons in this energy range is important, as they have a similar energy to 
the electrons produced when neutrinos from supernova bursts interact. In a 
LArTPC, at these energies, the energy deposition of electrons transitions 
between ionisation dominated and radiation dominated regimes, making for a 
unique event signature. The work presented in this thesis also details the 
selection and reconstruction of Michel electron events in \protodune{}, based 
on machine learning algorithms. Analysis of the reconstructed Michel electron 
events is used to quantify the energy resolution and bias for low energy 
electrons in \protodune{} based on this approach. The results of this analysis 
provide valuable inputs to studies of supernova burst neutrinos in LArTPC 
detectors.

In this thesis, chapter \ref{ch:neutrinophysics} provides a theoretical 
overview of neutrinos within the standard model. Interactions, oscillations, 
and production will be discussed summarising the current knowledge in this
field, as well as open questions which will be studied in ongoing and upcoming 
experiments. The role of neutrinos in supernova bursts and the detection of 
such neutrinos in a LArTPC detector will also be discussed in more detail.

The ProtoDUNE--SP experiment is described in Chapter \ref{ch:protodune},
including details of the beam line, detector, cosmic--ray flux, and simulations.
An overview of the LArTPC detection principle will be given with specific
details of the ProtoDUNE--SP design. Some details of detector operations will be
discussed, paying particular attention to the monitoring of the detector via the
online data quality monitoring system, which has been the author's major 
contribution to the detector operations.

Chapter \ref{ch:energyloss} will cover details of electromagnetic energy loss
in liquid argon. Electron and photon energy loss will be discussed as well as
processes leading to electron-ion recombination. The impacts of these effects on
electron reconstruction in liquid argon will be highlighted.

The main analyses of this thesis, which are discussed in Chapters 
\ref{ch:chargeid} and \ref{ch:michel}, make use of neural network algorithms 
for reconstruction, therefore, Chapter \ref{ch:ml} will briefly outline the 
relevant details of these algorithms.

Chapter \ref{ch:chargeid} will detail the development of a hit classification
algorithm based on convolutional neural networks. This algorithm is used to
classify hits as track--like or shower--like in \protodune{}, as well as to 
identify Michel electron hits. The results of this algorithm are currently being
used in a number of analyses of \protodune{} data, including the selection of 
Michel electron events, which is discussed in Chapter \ref{ch:michel}.

In Chapter \ref{ch:michel}, Michel electron reconstruction in \protodune{} will
be discussed. First, a brief overview of Michel electron production and energy 
loss in liquid argon will be given. This will be followed by a discussion of 
event selection and energy reconstruction algorithms, which were developed to 
study Michel electron events in \protodune{}. The reconstructed Michel electron 
spectrum will be compared between data and simulation, and the energy resolution
and bias for low energy electrons in the ProtoDUNE--SP detector will be 
estimated. Finally, the results will be compared to those from similar 
experiments, and their implications for DUNE will be highlighted.

A summary of the results will be given in Chapter \ref{ch:conclusion} along 
with a discussion of the implications of these results for physics in LArTPC 
detectors.
