This thesis and the work presented in it are my own and were produced by me as a
result of my own original research. Results and figures from published works by
others have been clearly attributed, and this work has not been submitted for
another qualification at this or any other university.

\medskip\noindent
After a brief introduction in Chapter \ref{ch:intro}, Chapter 
\ref{ch:neutrinophysics} gives an overview of the theory motivating the work 
presented in this thesis, which represents a summary of the work of others, for
which all relevant sources have been referenced. Similarly, Chapters
\ref{ch:energyloss} and \ref{ch:ml} represent a summary of the theory and tools
that are the foundations of the work in this thesis, and are the work of others.

\medskip\noindent
Chapter \ref{ch:protodune} describes the \protodune{} experiment, whose data was
analysed in this thesis. This chapter is predominantly a review of the work of
others; however, I made contributions to the development of the online 
monitoring system, for which I have included a statement outlining my 
contributions in Section \ref{sec:pdsp_om}.

\medskip\noindent
The development of the hit tagging algorithm based on a convolutional neural 
network in Chapter \ref{ch:chargeid} is my own work, as well as the analysis 
of the results for the \protodune{} beam particles and cosmic--rays. The hit 
reconstruction and clustering algorithms that led to the clustering of hits into
tracks and showers were developed by others, and the relevant documentation has 
been referenced. In the same way, Section \ref{cnn-appl} details the use of my 
hit tagging algorithm by others, whose work is referenced.

\medskip\noindent
The work on Michel electron reconstruction in Chapter \ref{ch:michel} and 
Appendix \ref{ch:energyfits} is my own. As with Chapter \ref{ch:chargeid}, this
work relies on the clustering algorithms developed by others. In addition, the 
energy calibration factors used in the Michel electron energy reconstruction
were calculated in the work of others.

\medskip\noindent
Finally, the conclusions presented in Chapter \ref{ch:conclusion} are my own.
